Further Evidence of Modified Spin-down in Sun-like Stars:\\Pile-ups in the Temperature--Period Distribution

### 2022-03-25 src/ms.tex
minor edits

We tested the hypothesis that the long-period pile-up observed in the \edit1{\lamostmcq} sample is due to WMB by fitting constant Rossby models to the \prot boundary. For a given \teff, this model predicts \prot as:

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{./figures/cmd.pdf}
    \caption{Gaia DR2 color-magnitude diagram. In each panel, a 2-d histogram of all Kepler targets is shown in grayscale, with lighter shades representing a higher number of targets in each cell. The estimated position of the Sun is indicated by the black point, based on the calibration of \citet{Casagrande2018}. In the middle and right panels, the \citet{Santos2021} targets with photometric rotation period detections are overplotted in orange. In the right panel, the CKS long-period pile-up stars identified in this work are shown by blue points and a Gaussian kernel density estimation of the \citet{Hall2021} asteroseismic sample is shown by blue contours.}
    \label{fig:cmd}
\end{figure*}

>>>>

We tested the hypothesis that the long-period pile-up observed in the \edit1{\lamostmcq} sample is \edit1{compatible with the} WMB \edit1{model} by fitting constant Rossby models to the \prot boundary. For a given \teff, this model predicts \prot as:

@@

\begin{figure*}
    \includegraphics[width=\linewidth]{./figures/cmd.pdf}
    \caption{Gaia DR2 color-magnitude diagram. In each panel, a 2-d histogram of all Kepler targets is shown in grayscale, with darker shades representing a higher number of targets in each cell. The estimated position of the Sun is indicated by the black point, based on the calibration of \citet{Casagrande2018}. In the middle and right panels, the \citet{Santos2021} targets with photometric rotation period detections are overplotted in orange. In the right panel, the CKS long-period pile-up stars identified in this work are shown by blue points and a Gaussian kernel density estimation of the \citet{Hall2021} asteroseismic sample is shown by blue contours.}
    \label{fig:cmd}
\end{figure*}
